О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Language issues to be resolved before publication
Rephrase a bit

\begin{definition}
	For given line segment $M_1 M_2$ and an integer $k$, $-|M_1 M_2| < k < |M_1 M_2|$,
	we define a $\rho(k,M_1 M_2)$-curve as the set of points $N$
	such that the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, a $\rho(k,M_1 M_2)$-curve is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.

@@

TODO: different vs. distinct

@@

>>>>

\begin{definition}
	For a line segment $M_1 M_2$ and an integer $k$, $-|M_1 M_2| < k < |M_1 M_2|$,
	we define a $\rho(k,M_1 M_2)$-curve as the set of points $N$
	for which the equality $|N M_1| - |N M_2| = k$ holds.
\end{definition}
So, in the planar case a $\rho(k,M_1 M_2)$-curve
is a branch of a hyperbola for $k\neq 0$ and the bisector of line segment $M_1 M_2$ for $k=0$.

@@

@@

\section{Language issues to be resolved before publication}

\begin{enumerate}
	\item
		there are at most $2k-1$ distinct segments $\Delta_i$

		different vs. distinct ?

	\item
		Summing up

		is it correct to say so ?

	\item
		... the following \\ Theorem X.

		is it correct to split the sentence in such a way?

	\item
		For the sake of completeness.

		Is the phrase correct?
		There should be an example in one of papers about Banach limits...

	\item
		to belong vs. to be situated

	\item
		intersection of ... and ...
		OR
		intersection of ... with ...
		?

\end{enumerate}
